Emittance preservation of an electron beam in a loaded quasi-linear plasma wakefield

### 2017-10-09 Tex/Paper.tex
Added beam offset plot

@@

\begin{figure}[hbt]
    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQuality}
    \caption{\label{Fig:BeamQ} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$, as a function
        of initial beam charge (blue symbols, lines), and relative energy spread of the accepted charge (red symbols,
        dashed lines), after $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.
        These are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies
        presented in beam loading section correspond to the square marked lines at $100\unit{pC}$.}
\end{figure}

\begin{figure}[hbt]
    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityAbs}
    \caption{\label{Fig:BeamQAbs} Witness beam charge with emittance preserved, $\widetilde{Q}$, as a function of
        initial beam charge (blue symbols, lines), and final energy (red symbols, dashed lines), after $4\unit{m}$ of
        plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
\end{figure}

@@

Figure~\ref{Fig:BeamQAbs} shows the dependence of mean energy gain on beam length and beam charge (red curves). The blue
curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as a function of
beam length and beam charge.

\begin{figure}[hbt]
    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
    \caption{\label{Fig:BeamQEmit} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$, as a
        function of initial emittance (blue symbols, line), and relative energy spread of the accepted charge (red
        symbols, dashed line), after $4\unit{m}$ of plasma.}
\end{figure}

>>>>

\begin{figure*}[hbt]
    \includegraphics[width=0.49\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQuality}
    \includegraphics[width=0.49\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityAbs}
    \caption{\label{Fig:BeamQ} Left: Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$, as a function
        of initial beam charge (blue symbols, lines), and relative energy spread of the accepted charge (red symbols,
        dashed lines), after $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.
        These are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies
        presented in beam loading section correspond to the square marked lines at $100\unit{pC}$.
        Right: Witness beam charge with emittance preserved, $\widetilde{Q}$, as a function of
        initial beam charge (blue symbols, lines), and final energy (red symbols, dashed lines), after $4\unit{m}$ of
        plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
\end{figure*}

@@

\begin{figure*}[hbt]
    \includegraphics[width=0.49\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityOffset}
    \includegraphics[width=0.49\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
    \caption{\label{Fig:BeamQEmit} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$
        (blue symbols, line), as a function of beam offset (left) and initial emittance (right), with relative energy
        spread of the accepted charge (red symbols, dashed line), after $4\unit{m}$ of plasma.}
\end{figure*}

@@

Figure~\ref{Fig:BeamQ} shows the dependence of mean energy gain on beam length and beam charge (red curves). The blue
curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as a function of
beam length and beam charge.
